Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-02-11 supplement.tex
Weave a story in the supplement

As in the main article, all the figures shown in this section are shown as-is, 
without any aesthetical modifications, with the exception that the arrangement
of the sub-figures (for example, aligning true and twin tree
horiztonally) is done manually.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Generative model only}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_1}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{pirouette_example_1/example_1_314/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{pirouette_example_1/example_1_314/true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{pirouette_example_1/example_1_314/true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{pirouette_example_1/example_1_314/true_error_violin_gen.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Generative model only: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{pirouette_example_1/example_1_314/esses_gen.latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparing to other candidate models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_2}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.7\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.5\textheight]{pirouette_example_2/example_2_314/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.5\textheight]{pirouette_example_2/example_2_314/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.45\textheight]{pirouette_example_2/example_2_314/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_2/example_2_314/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.45\textheight]{pirouette_example_2/example_2_314/true_posterior_best.png}
    };   
    \node[state] (DB) [right of = DG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_2/example_2_314/true_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Comparing to other candidate models: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{pirouette_example_2/example_2_314/esses_gen.latex}

\input{pirouette_example_2/example_2_314/esses_best.latex}

\input{pirouette_example_2/example_2_314/evidence_true.latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparing to background noise}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_3}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {1.0\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.5\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.4\textheight]{pirouette_example_3/example_3_314/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.25\textheight]{pirouette_example_3/example_3_314/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.4\textheight]{pirouette_example_3/example_3_314/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.25\textheight]{pirouette_example_3/example_3_314/twin_alignment.png}
    };   
    \node[state] (CTG) [right of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_3/example_3_314/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Comparing to background noise: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{pirouette_example_3/example_3_314/esses_gen.latex}

\input{pirouette_example_3/example_3_314/esses_best.latex}

\input{pirouette_example_3/example_3_314/esses_twin_gen.latex}

\input{pirouette_example_3/example_3_314/esses_twin_best.latex}

\input{pirouette_example_3/example_3_314/evidence_true.latex}

\input{pirouette_example_3/example_3_314/evidence_twin.latex}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_17}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_17/example_17_314/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3/example_3_314/errors.png}
  \caption{Equal number of mutations}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_18/example_18_314/errors.png}
  \caption{Equal mutation rate}
\end{figure}

>>>>

All the figures shown in this section are shown as-is, 
without any aesthetical modifications, with the exception that the arrangement
of the sub-figures (for example, aligning true and twin tree
horizontally) is done manually.

First, subsection \ref{subsec:main_example} shows extra figures and
 diagnostics regarding the main example. Because the main example
only uses one exemplary tree, subsection \ref{subsec:distribution}
shows the result of using multiple trees, as generated by the
same stochastic process as the main example.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main example}
\label{subsec:main_example}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\richel{Issue \url{https://github.com/richelbilderbeek/pirouette_article/issues/75}}

This subsection shows the diagnostics from the main example, which
uses one tree.
The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_30}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {1.0\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.5\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.4\textheight]{pirouette_example_30/example_30_314/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.25\textheight]{pirouette_example_30/example_30_314/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.4\textheight]{pirouette_example_30/example_30_314/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.25\textheight]{pirouette_example_30/example_30_314/twin_alignment.png}
    };   
    \node[state] (CTG) [right of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {
      \includegraphics[height=0.3\textheight]{pirouette_example_30/example_30_314/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_30_full_pipeline}
  \caption{Comparing to background noise: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{pirouette_example_30/example_30_314/esses_gen.latex}

\input{pirouette_example_30/example_30_314/esses_best.latex}

\input{pirouette_example_30/example_30_314/esses_twin_gen.latex}

\input{pirouette_example_30/example_30_314/esses_twin_best.latex}

\input{pirouette_example_30/example_30_314/evidence_true.latex}

\input{pirouette_example_30/example_30_314/evidence_twin.latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Using a distribution of trees}
\label{subsec:distribution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\richel{Issue \url{https://github.com/richelbilderbeek/pirouette_article/issues/89}}

This subsection extends the main example, by using multiple (instead of
one) trees. These trees are produced by running a DD tree simulation
with the same parameters as the main example, which are
speciation rate \richel{?}, extinction rate $0.1$, and carrying
capacity 40.

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_28}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/example_28_314/errors.png}
  \caption{Error distribution from a distribution of trees}
\end{figure}

@@

The code used in this part of the article can be found at 
\url{https://github.com/richelbilderbeek/pirouette_example_3007}.

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3007/example_17_314/errors.png}
  \caption{An unliked node substitution model}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/example_30_314/errors.png}
  \caption{Equal number of mutations}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_3008/example_18_314/errors.png}
  \caption{Equal mutation rate}
\end{figure}
